%Two resources useful for abstract writing.
% Guidance of how to write an abstract/summary provided by Nature: https://cbs.umn.edu/sites/cbs.umn.edu/files/public/downloads/Annotated_Nature_abstract.pdf %https://writingcenter.gmu.edu/guides/writing-an-abstract
\chapter*{\center \Large  Abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Replace all text with your text
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
This study explores tree genus classification using Sentinel-2 imagery, focusing on seasonal and spectral band combinations and incorporating additional environmental data. The analysis revealed that the model performs best during summer and autumn, where clear spectral signatures enhance accuracy. The optimal spectral band combination was found to be B3, B6, B8, and B11, balancing classification performance with storage efficiency. Although integrating soil composition and elevation provided marginal improvements, Sentinel-2’s high-resolution spectral data was most influential. Climate data from the ECMWF Reanalysis v5 (ERA5) showed minimal short-term impact on classification over five years, with the study’s European focus possibly limiting broader applicability. Attempts to model climate change effects using a regression neural network yielded poor results, highlighting the complexity of capturing such relationships. Future research should prioritize long-term data analysis to better understand gradual climate effects, consider regions with more pronounced climate changes, and differentiate between commercial and natural forests to reveal distinct change patterns. Incorporating additional environmental variables and collaborating with ecologists could further enhance model accuracy and insights into tree genus distributions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%s
~\\[1cm]
\noindent % Provide your key words
\textbf{Keywords:} Convolutional Neural Network (CNN), Sentinel-2, Copernicus, SoilGrid, EU-Forest, Forests, Tree Genus, Climate, ERA5

\vfill
\noindent
\textbf{Report's total word count:} 6000-7000